Screen Time Review of Reviews Summary

### 2021-08-18 index.Rmd

```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
comparison_plots$`health behaviour`
```

@@

```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
comparison_plots$`physical health`
```

@@

```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
comparison_plots$psychology
```

@@

```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
comparison_plots$education
```

>>>>

```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=15}
comparison_plots$`health behaviour`
```

@@

```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=15}
comparison_plots$`physical health`
```

@@

```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=15}
comparison_plots$psychology
```

@@

```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=15}
comparison_plots$education
```
